Portfolio prioritization of salmon conservation

### 2013-03-19 inst/examples/salmonport.Rmd
Updating files before major work after Jon, Andy, Trevor meetings

# Abstract
First part is copied from what I wrote before (introduction and questions). Second part outlines the simulation. I haven't yet worked very much with the portfolios themselves, but I've set up the structure of the simulation. I outline how the simulation is currently working and show examples of some of the plotting functions I have to look at simulation and portfolio optimization.

# Introduction
[Based partly on Jon's notes.] Managing risk is fundamental to the conservation of an endangered species. When an endangered species exists as a metapopulation, we can manage risk at two levels: at the population level or at the metapopulation level. Typically we treat sources of risk at the metapopulation level as external and uncontrollable and so we manage risk by altering anthropogenic disturbances such as fishing or hunting on a population level as well as improving connectivity of populations.

The management of financial portfolios provides another way of considering risk. Economists consider the risk and performance of a financial portfolio as depending on the weighting of individual assets that make up the portfolio. Modern Portfolio Theory (MPT) proposes that there is a set of portfolios that achieves maximum expected return for a level of expected risk or minimum expected risk for a level of expected return [@Markowitz1952; @Markowitz1959]. This optimal set contains portfolios that range along a continuum of risk-tolerance; economists refer to this set as the efficient frontier.

Similarly, expected growth rate and variance at a metapopulation level will be a function of the properties of the populations. A portfolio approach to managing risk for a metapopulation therefore considers how conservation might affect the ``weight'' of each population in the metapopulation ``portfolio''.

@@

## Portfolio prioritization of salmon conservation
Here, we conduct a post-hoc assessment of the set of optimal salmon portfolios given various return-risk definitions and objectives. We ask: What does a portfolio approach to management tell us about salmonid conservation priorities? Does it produce any rules of thumb about what optimal portfolio management of salmonid metapopulations would entail?

## Questions
1. What are the attributes of the populations that form the optimal set? For example, are populations with high response diversity prioritized?

@@

3. How do our answers to other questions change depending on what we measure on the risk-return axes? For example, we could trade off the mean rate of change of salmon returns vs.\ variance of the rate of change. This would be most similar to a financial portfolio optimization. We could also trade off the salmon returns (or catches) themselves. Further, we could work with variance or a downside risk metric like CVaR.

4. How do constraints (e.g.\ viable salmonid population (VSP)-like constraints) affect the selected portfolios in risk-return space and in terms of common metrics such as population-level and ESU-level extinction risk?

@@

Simulation
==========
See Figure \ref{fig:sim-diagram} for an illustration of the simulation 
structure.

\begin{figure}[htbp]
  \centering
    \includegraphics[height=7in]{simulation_diagram.pdf}
 \caption{Flow chart of the salmon-metapopulation simulation and portfolio optimization. There are $n$ salmon populations and $t$ generations. Blue text indicates values that are generated before the simulation progresses through time. Orange text indicates steps in which calculations are performed. Black text indicates values that are calculated. Grey text indicates parameters that can be set. Green text indicates the looping structure of the simulation.}
  \label{fig:sim-diagram}
\end{figure}

## Spawner-return relationship
I am using a Ricker curve,

@@

\noindent
where $t$ represents a generation time, $i$ represents a population, $R$ is the number of returns, $S$ is the number of spawners, $a$ is the productivity parameter (which can vary with the environmental signal), and $b$ is the density-dependent term (which is used as the asset weights in the portfolios). The term $w_{ti}$ represents first-order autocorrelated error (AR1). Formally, $w_{ti} = w_{ti-1} \rho + v_{ti}$, where $v_{ti}$ represents independent and normally distributed error with mean 0 and standard deviation of $\sigma_v$. The parameter $\rho$ represents the correlation between residuals from subsequent years.

## Escapement targets
I am calculating spawning abundance MSY $S_{MSY}$ each generation using the equation $S_{MSY} = b(0.5-0.07a)$ from @Hilborn1992 p272, Table 7.2. I am using the precisely known $a$ and $b$ values each time and assume perfect implementation of the escapement goal (no outcome uncertainty) and no upper limit on how much the fishery can harvest. We may want to add a bit of noise here, say by assuming a constant value for $a$ or adding some implementation uncertainty. We need some level of harvesting to keep the spawning population away from carrying capacity. At carrying capacity, the productivity parameter $a$ has minimal effect on population dynamics, making it a poor way to integrate response diversity.

## Environmental signal
I have programmed five different kinds of environmental signals. I think it's easiest to think of these as temperature signals, but they could represent more general environmental anomalies, such as the PDO. The five kinds of environmental signals are described in Table \ref{tab:env-types} and illustrated in Figure \ref{fig:env-ts}. Later, I may include black-swan-like events, although the regime shifts could be seen this way if the changes are dramatic enough. So far all figures use a sine wave. The problem with using a randomly generated ARMA time series is that you get much greater differences in the portfolios from 
run to run.

\begin{table}[h!]
  \centering
  \small
  \caption{Environmental signals, parameters, and descriptions.}
\begin{tabular}{p{3.2cm}p{3.25cm}p{6.8cm}}
\toprule
Signal type & Parameters & Description \\
\midrule
Sine wave & $\overline{T} + A \cdot \sin(\omega t + \phi)$& $\overline{T}$ is 
the mean environmental value, $A$ is the amplitude, $\omega$ is the frequency in 
radians, and $\phi$ is the phase\\
ARMA & AR1, MA1, $\sigma_T$ & First-order autoregressive (AR1) and moving 
average (MA1) parameters and standard deviation; mean is assumed to be 0\\
Regime shifts & $T_{b0},T_{b1}, \ldots, T_{bn}$; $T_{v0},T_{v1}, \ldots, T_{vn}$ 
& Breakpoints ($T_{b}$) and values ($T_v$) for regimes $1$ through $n$\\
Linear change & $T_{\mathrm{min}}$, $T_{\mathrm{max}}$ & Minimum and maximum 
values\\
Constant & $T_{\mathrm{constant}}$& Constant value\\
\bottomrule
\end{tabular}
\label{tab:env-types}
\end{table}

```{r env-ts, fig.height=5, fig.width=4, fig.cap="Example temperature time series\\label{fig:env-ts}"}
source("plot_env_ts.R")
col_pal <- rev(gg_color_hue(10))
```

## Straying
[Insert a bit here about my research on straying and it's influence on metapopulation dynamics for salmon]. Essentially, straying should be enough to prevent local extinctions and ensure all possible habitat is occupied, but probably not strong enough to noticeably affect population dynamics or synchrony [@Schtickzelle2007].

I've implemented straying as in @Cooper1999. I generate a matrix that represents the fraction of straying between any two populations. I have set up the metapopulation (thus far) as in in a very simple scenario: the populations are arranged in a line and those that are nearer to each other are more likely to stray between each other [insert caveats]. Two parameters control the straying: the fraction of fish that stray from their natal stream in any given generation $f$ and the rate at which this straying between streams decays with distance $m$. I calculated the number of salmon straying from stream $i$ to stream $j$ as,

\begin{equation}
  \mathrm{strays}_{tij} = \frac{S_{ti} f e^{-m \lvert i-j \rvert }}{\sum\limits_{k \neq j}^{} e^{-m \lvert k-j \rvert }},
\end{equation}

where the denominator is a normalization constant to ensure that no salmon are gained or lost. The subscript $k$ represents a stream ID. [Not sure this is written correctly --- I'll think about it --- but it should be coded correctly.] There is no straying from and to the same stream. See Figure \ref{fig:stray-matrix} for an example straying matrix.

@@

## Diversity of response to the environmental conditions
[insert research I've done here on what can generate diversity of response to the environment across populations and how it is typically incorporated] This is a critical part to the paper.

@@

I calculate $a_{ti}$, the realized Ricker productivity parameters after accounting for thermal tolerance, as

\begin{equation}
  a_{ti} = a_i^* + \gamma_i (T_t - T_i^*)^2,
\end{equation}

where $a_i^*$ is the maximum possible productivity parameter for population $i$, $T_t$ is the temperature at time step $t$, $T_i^*$ is the optimal temperature for population $i$, and $\gamma_i$ controls the width of the thermal tolerance curve for each population. See Figure \ref{fig:thermal-curves} for the default thermal tolerance curves for ten populations.

@@

```{r thermal-curves, cache=FALSE, fig.height=3.9, fig.width=5.4, fig.cap="Thermal tolerance curves for ten populations. Here, and throughout this document, I have used the same rainbow of colours to identify the salmon populations. The populations are arranged from blue (more productive with cooler temperatures) to red (more productive with warmer temperatures\\label{fig:thermal-curves}"}
source("plot_thermal_curves.R")
```

Portfolio optimization
======================
Details to follow. Quick version: I Monte Carlo the $b$ parameters (with a specified minimum value) and measure the resulting mean and variance of the rate of growth of the metapopulation salmon returns. I then identify the set of $b$ parameters (i.e.\ the set of weights) that results in the efficient frontier. We could later choose to work with risk metrics like conditional value at risk (CVaR), which measure the probability of a ``bad'' event specifically, not the symmetrical variance.

@@

Comparing portfolios
====================
This is a big area to think about. How do portfolios differ along the frontier? How do the frontier portfolios differ from non-frontier portfolios? What is the best way to visually compare them? What aspects to compare? Are there summary statistics we could use to compare them?

Some sample simulations
=======================
The following are options and their default values:

\begin{verbatim}
  n_t = 120, # number of years
  n_pop = 10, # number of populations
  stray_decay_rate = 0.3, # rate that straying decays with distance
  stray_fraction = 0.01, # fraction of fish that stray from natal streams
  b = rep(1000, n_pop), # Ricker density-dependent parameter
  spawners_0 = round(b), # spawners at start
  sigma_v = 0.1, # stock-recruit residual SD
  v_rho = 0.4, # stock-recruit residual AR1 correlation
  a_width_param = rep(0.02, n_pop), # width of thermal curves by pop
  optim_temp = seq(13, 19, length.out = n_pop), # optimal temperatures by pop
  max_a = rep(1.4, n_pop), # maximum Ricker a values by pop at optimum temp
  env_type = c("sine", "arma", "regime", "linear", "constant"),
  env_params = list(amplitude = 2.0, ang_frequency = 0.2, phase = 0, mean_value = 16),
  use_cache = FALSE, # regenerate stochastic values? 
  add_straying = TRUE # include or ignore straying
\end{verbatim}

@@

```{r run-base-example1, fig.height=6.5, fig.width=5, fig.cap="Example simulation with all parameters at default values. I'm only showing a sample of 40 generations (after the burn-in period). From top to bottom: salmon returns each generation (catch plus escapement); Ricker $a$ parameter; the environmental signal (could think of it as temperature or a composite environmental signal like the PDO); number of salmon straying by population; number of straying salmon being received by population; fisheries catch based on escapement MSY calculation; salmon escapement; residuals from the spawner-return curve."}
set.seed(2)
eg1 <- meta_sim(b = rep(1000, 10), n_pop = 10)
plot_sim_ts(eg1, years_to_show = 40)
```

```{r plot-base-corrs, fig.width=4, fig.height=4, fig.cap="A plot comparing the log(returns) between each population. The population colours and numbers match in all figures. Note how populations 1 and 10 have asynchronous returns whereas populations with more similar thermal-tolerance curves (say populations 9 and 10) have more synchronous dynamics. Populations with thermal tolerance curves in the middle (e.g.\ population 6) are less correlated with other populations. Their population dynamics end up primarily driven by demographic stochasticity and less so by temperature-induced systematic changes in productivity."}
plot_correlation_between_returns(eg1, pal = col_pal)
```

```{r plot-base-rickers, fig.width=8, fig.height=5, cache=FALSE, fig.cap="We can also look at samples of the Ricker curves by population (population numbers are in the upper left corners). Here, I've sampled 40 of the $a$ parameters through time for each population. The shaded rectangles to indicate the range of spawners observed in the simulation. The colour of the line indicates the temperature anomaly in that year with blue indicating cooler years and red indicating warmer years. In this example all the populations have the same $b$ parameters. Notice how the productivity is more variable for populations nearer the limits of their thermal tolerance (e.g.\ population 1 vs.\ population 5). Also notice how population 1 is more productive in cool years whereas population 10 is more productive in warm years."}
plot_rickers(eg1, pal = col_pal)
```

@@

An example of portfolio optimization
====================================
Now, let's run an example where we find the $b$ values that form the efficient frontier of metapopulation portfolios.

```{r set-a-seed, echo=FALSE}
set.seed(3)
```

```{r monte-carlo-portfolios}
weights_matrix <- create_asset_weights(n_pop = 10, n_sims = 100, 
  weight_lower_limit = 0.01)
mc_ports <- monte_carlo_portfolios(weights_matrix = weights_matrix,
  n_sims = 100, mean_b = 1000)
```

@@

```{r fig.width=8, fig.height=5, fig.cap="Example Ricker curves for the minimum-variance metapopulation."}
plot_rickers(min_var_sim, pal = col_pal)
```

```{r plot-portfolio-timeseries, fig.width=6.5, fig.height=3.5, fig.cap="Time series for a random sample of portfolios (grey lines) and the minimum-variance portfolio (white lines). The top panel shows rate of change or metapopulation abundance at each time step and the bottom panel shows the metapopulation abundance."}
source("plot_portfolio_ts.R")
```

@@

References
==========

>>>>

# Abstract #
First part is copied from what I wrote before (introduction and questions). Second part outlines the simulation. I haven't yet worked very much with the portfolios themselves, but I've set up the structure of the simulation. I outline how the simulation is currently working and show examples of some of the plotting functions I have to look at simulation and portfolio optimization.

# Introduction #
Managing risk is fundamental to the conservation of an endangered species. When an endangered species exists as a metapopulation, we can manage risk at two levels: at the population level or at the metapopulation level. Typically we treat sources of risk at the metapopulation level as external and uncontrollable and so we manage risk by altering fishing or hunting on a population level as well as improving the connectivity of populations.

The management of financial portfolios provides another way of considering risk. Economists consider the risk and performance of a financial portfolio as a function of the weighting of individual assets that make up the portfolio. Modern Portfolio Theory (MPT) proposes that there is a set of portfolios that maximizes expected return for a level of expected risk or minimizes expected risk for a level of expected return [@Markowitz1952; @Markowitz1959]. This optimal set contains portfolios that range along a continuum of risk-tolerance; economists refer to this set as the efficient frontier.

Similarly, expected growth rate and variance at a metapopulation level is a function of the variance, covariance, and size of the individual populations. A portfolio approach to managing risk for a metapopulation therefore considers how conservation might affect the "weight" of each population in a metapopulation "portfolio".

@@

## Portfolio prioritization of salmon conservation ##
The basic goal is to conduct a post-hoc assessment of the set of optimal salmon portfolios given various return-risk definitions and objectives. We ask: What does a portfolio approach to management tell us about salmonid conservation priorities? Can we produce any rules of thumb about what optimal portfolio management of salmonid metapopulations would entail?

## Questions ##
1. What are the attributes of the populations that form the optimal set? For example, does the optimal set tend to focus on populations with as diverse responses to the environment as possible?

@@

3. How do our answers to other questions change depending on what we measure on the risk-return axes? For example, we could trade off the mean rate of change of salmon returns vs. variance of the rate of change. This would be most similar to a financial portfolio optimization. We could also trade off the salmon returns (or catches) themselves. Further, we could work with variance or a downside risk metric like CVaR.

4. How do constraints (e.g. viable salmonid population (VSP)-like constraints) affect the selected portfolios in risk-return space and in terms of common metrics such as population-level and ESU-level extinction risk?

@@

# Simulation #
See Figure \ref{fig:sim-diagram} for an illustration of the simulation 
structure.

\begin{figure}[htbp]
  \centering
    \includegraphics[height=6.5in]{simulation_diagram.pdf}
 \caption{Flow chart of the salmon-metapopulation simulation and portfolio optimization. There are $n$ salmon populations and $t$ generations. Blue text indicates values that are generated before the simulation progresses through time. Orange text indicates steps in which calculations are performed. Black text indicates values that are calculated. Grey text indicates parameters that can be set. Green text indicates the looping structure of the simulation.}
  \label{fig:sim-diagram}
\end{figure}

## Spawner-return relationship ##
I am using a Ricker curve,

@@

\noindent
where $t$ represents a generation time, $i$ represents a population, $R$ is the number of returns, $S$ is the number of spawners, $a$ is the productivity parameter (which can vary with the environmental signal), and $b$ is the density-dependent term (which is used as the asset weights in the portfolios). The term $w_{ti}$ represents first-order autocorrelated error (AR1). Formally, $w_{ti} = w_{ti-1} \rho + v_{ti}$, where $v_{ti}$ represents independent and normally distributed error with mean 0 and standard deviation of $\sigma_v$. The parameter $\rho$ represents the correlation between residuals from subsequent generations.

## Escapement targets ##
I am calculating spawning abundance MSY $S_{MSY}$ each generation using the equation $S_{MSY} = b(0.5-0.07a)$ from @Hilborn1992 p272, Table 7.2. I am using the precisely known $a$ and $b$ values each time and assume perfect implementation of the escapement goal (no outcome uncertainty) and no upper limit on how much the fishery can harvest. We may want to add a bit of noise here, say by assuming a constant value for $a$ or adding some implementation uncertainty. We need some level of harvesting to keep the spawning population away from carrying capacity. At carrying capacity, the productivity parameter $a$ has minimal effect on population dynamics, making it a poor way to integrate response diversity.

## Environmental signal ##
I have programmed five different kinds of environmental signals. I think it's easiest to think of these as temperature, but they could represent more general environmental anomalies, such as the PDO. In Table \ref{tab:env-types}, I describe the five kinds of environmental signals I have included. Examples of these time series are illustrated in Figure \ref{fig:env-ts}. Later, I may include black-swan-like events, although the regime shifts could be seen this way if the changes are dramatic enough. So far, all simulation results in the rest of this document use a sine wave. The problem with using a randomly generated ARMA time series is that you get much greater differences in the results from 
run to run. This is fine in the long run, but hard to detect patterns initially.

\begin{table}[h!]
\centering
\small
\caption{Environmental signals, parameters, and descriptions.}
\begin{tabular}{p{3.2cm}p{3.25cm}p{6.8cm}}
\toprule
Signal type & Parameters & Description \\
\midrule
Sine wave & $\overline{T} + A \cdot \sin(\omega t + \phi)$& $\overline{T}$ is 
the mean environmental value, $A$ is the amplitude, $\omega$ is the frequency in 
radians, and $\phi$ is the phase\\
ARMA & AR1, MA1, $\sigma_T$ & First-order autoregressive (AR1) and moving 
average (MA1) parameters and standard deviation; mean is assumed to be 0\\
Regime shifts & $T_{b0},T_{b1}, \ldots, T_{br-1}$; $T_{v0},T_{v1}, \ldots, T_{vr}$ 
& Breakpoints ($T_{b}$) and values ($T_v$) for regimes $1$ through $r$\\
Linear change & $T_{\mathrm{min}}$, $T_{\mathrm{max}}$ & Minimum and maximum 
values\\
Constant & $T_{\mathrm{constant}}$& Constant value\\
\bottomrule
\end{tabular}
\label{tab:env-types}
\end{table}

```{r env-ts, fig.height=4, fig.width=4, cache = FALSE, fig.cap="Example temperature time series\\label{fig:env-ts}"}
# library(metafolio)
# or for rapid development:
metafolio_files <-  list.files(path = "../../R/")
for(i in 1:length(metafolio_files)){
  source(paste("../..//R/", metafolio_files[i], sep = ""));rm(i)}

source("plot_env_ts.R")
col_pal <- rev(gg_color_hue(10))
```

## Straying ##
[Insert a bit here about my research on straying and it's influence on metapopulation dynamics for salmon]. Essentially, straying should be enough to prevent local extinctions and ensure all possible habitat is occupied, but probably not strong enough to noticeably affect population dynamics or synchrony [@Schtickzelle2007].

I've implemented straying as in @Cooper1999. I generate a matrix that represents the fraction of straying between any two populations. I have set up the metapopulation (thus far) in a very simple scenario: the populations are arranged in a line and those that are nearer to each other are more likely to stray between each other [insert caveats]. Two parameters control the straying: the fraction of fish $f$ that stray from their natal stream in any given generation and the rate at which this straying between streams decays with distance $m$. I calculated the number of salmon straying from stream $j$ to stream $i$ as,

\begin{equation}
  \mathrm{strays}_{tij} = f R_{tj} \frac{e^{-m \lvert i-j \rvert }}{\displaystyle\sum\limits_{\substack{k = 1 \\
  k \neq j}}^{n} e^{-m \lvert k-j \rvert }},
\end{equation}

\noindent
where $R_{tj}$ is the number of returning salmon at generation $t$ whose natal stream was stream $j$. The subscript $k$ represents a stream ID and $n$ the number of populations. The denominator is a normalizing constant to ensure the desired fraction of fish stray. See Figure \ref{fig:stray-matrix} for an example straying matrix.

@@

## Diversity of response to the environmental conditions ##
[insert research I've done here on what can generate diversity of response to the environment across populations and how it is typically incorporated] This is a critical part to the paper.

@@

I calculate $a_{ti}$, the realized Ricker productivity parameters after accounting for thermal tolerance, as
\begin{equation}
  a_{ti} = a_i^* + \gamma_i (T_t - T_i^*)^2,
\end{equation}
\noindent
where $a_i^*$ is the maximum possible productivity parameter for population $i$, $T_t$ is the temperature at time step $t$, $T_i^*$ is the optimal temperature for population $i$, and $\gamma_i$ controls the width of the thermal tolerance curve for each population. See Figure \ref{fig:thermal-curves} for the default thermal tolerance curves for ten populations.

@@

```{r thermal-curves, fig.height=3.7, cache = FALSE, fig.width=5.0, fig.cap="Thermal tolerance curves for ten populations. Here, and throughout this document, I have used the same rainbow of colours to identify the salmon populations. The populations are arranged from blue (more productive with cooler temperatures) to red (more productive with warmer temperatures).\\label{fig:thermal-curves}"}
source("plot_thermal_curves.R")
```

# Portfolio optimization #
Details to follow. Quick version: I Monte Carlo the $b$ parameters (with a specified minimum value) and measure the resulting mean and variance of the rate of growth of the metapopulation salmon returns. I then identify the set of $b$ parameters (i.e. the set of weights) that results in the efficient frontier. We could later choose to work with risk metrics like conditional value at risk (CVaR), which measure the probability of a ``bad'' event specifically, not the symmetrical variance.

@@

# Comparing portfolios #
This is a big area to think about. How do portfolios differ along the frontier? How do the frontier portfolios differ from non-frontier portfolios? What is the best way to visually compare them? What aspects to compare? Are there summary statistics we could use to compare them?

# Some sample simulations #
The following are options and their default values:

    n_t = 120, # number of generations
    n_pop = 10, # number of populations
    stray_decay_rate = 0.3, # rate that straying decays with distance
    stray_fraction = 0.01, # fraction of fish that stray from natal streams
    b = rep(1000, n_pop), # Ricker density-dependent parameter
    spawners_0 = round(b), # spawners at start
    sigma_v = 0.1, # stock-recruit residual SD
    v_rho = 0.4, # stock-recruit residual AR1 correlation
    a_width_param = rep(0.02, n_pop), # width of thermal curves by pop
    optim_temp = seq(13, 19, length.out = n_pop), # optimal temperatures by pop
    max_a = rep(1.4, n_pop), # maximum Ricker a values by pop at optimum temp
    env_type = c("sine", "arma", "regime", "linear", "constant"),
    env_params = list(amplitude = 2.0, ang_frequency = 0.2, phase = 0, mean_value = 16),
    use_cache = FALSE, # regenerate stochastic values? 
    add_straying = TRUE # include or ignore straying

@@

```{r run-base-example1, fig.height=6.5, fig.width=5, fig.cap="Example simulation with all parameters at default values. I'm only showing a sample of 40 generations (after the burn-in period). From top to bottom: salmon returns each generation (catch plus escapement); Ricker $a$ parameter; the environmental signal (could think of it as temperature or a composite environmental signal like the PDO); number of salmon straying by population; number of straying salmon being received by population; fisheries catch based on escapement MSY calculation; salmon escapement; residuals from the spawner-return curve."}
set.seed(2)
eg1 <- meta_sim(b = rep(1000, 10), n_pop = 10)
plot_sim_ts(eg1, years_to_show = 40)

o <- meta_sim(env_params = list(amplitude = .000000001, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.01, n_pop = 10, stray_fraction = 0.00001, use_cache = FALSE)
o <- meta_sim(env_params = list(amplitude = .000000001, ang_frequency = 0.2, phase = 0, mean_value = 16), sigma_v = 0.1, n_pop = 10, stray_fraction = 0.00001, use_cache = FALSE)
#o<- meta_sim(b = rep(1000, 10), n_pop = 10)
plot_sim_ts(o, years_to_show = 60)
image(o$Est_b)
```

```{r plot-base-corrs, fig.width=4, fig.height=4, fig.cap="A plot comparing the log(returns) between each population. The population colours and numbers match in all figures. Note how populations 1 and 10 have asynchronous returns whereas populations with more similar thermal-tolerance curves (say populations 9 and 10) have more synchronous dynamics. Populations with thermal tolerance curves in the middle (e.g. population 6) are less correlated with other populations. Their population dynamics end up primarily driven by demographic stochasticity and less so by temperature-induced systematic changes in productivity."}
plot_correlation_between_returns(eg1, pal = col_pal)
```

```{r plot-base-rickers, fig.width=6, fig.height=3.75, cache=FALSE, fig.cap="We can also look at samples of the Ricker curves by population (population numbers are in the upper left corners). Here, I've sampled 40 of the $a$ parameters through time for each population. The shaded rectangles to indicate the range of spawners observed in the simulation. The colour of the line indicates the temperature anomaly in that year with blue indicating cooler years and red indicating warmer years. In this example all the populations have the same $b$ parameters. Notice how the productivity is more variable for populations nearer the limits of their thermal tolerance (e.g. population 1 vs. population 5). Also notice how population 1 is more productive in cool years whereas population 10 is more productive in warm years."}
plot_rickers(eg1, pal = col_pal)
```

@@

# An example of portfolio optimization #
Now, let's run an example where we find the $b$ values that form the efficient frontier of metapopulation portfolios.

```{r set-a-seed, echo=FALSE}
set.seed(1)
```

```{r monte-carlo-portfolios}
weights_matrix <- create_asset_weights(n_pop = 10, n_sims = 100, 
  weight_lower_limit = 0.001)
mc_ports <- monte_carlo_portfolios(weights_matrix = weights_matrix,
  n_sims = 100, mean_b = 1000)
```

@@

```{r fig.width=6, fig.height=3.75, fig.cap="Example Ricker curves for the minimum-variance metapopulation."}
plot_rickers(min_var_sim, pal = col_pal)
```

```{r plot-portfolio-timeseries, fig.width=6, fig.height=3.5, fig.cap="Time series for a random sample of portfolios (grey lines) and the minimum-variance portfolio (white lines). The top panel shows rate of change or metapopulation abundance at each time step and the bottom panel shows the metapopulation abundance."}
source("plot_portfolio_ts.R")
```

```{r plot-weights-samples, fig.width=6, fig.height=6, fig.cap="A sample of 30 minimum-variance portfolios given the same set of starting parameters as for the example illustrated above. The dashed grey line indicates the weights if all populations had an equal carrying capacity. As it stands, the weights look fairly random to me."}
source("look_at_cluster_dat.R")
```

```{r plot-weights-median, fig.width=4.2, fig.height=3.2, cache = FALSE, fig.cap="Median (solid line) and 25th and 75th quantiles of the weights across 40 minimum-variance portfolios. Just another way of looking at it."}
source("min_var_ports_dist.R")
```

@@

# Notes #
- b is "unfished equilibrium stock size"

```{r}
```

# References #
